CommonMind Consortium: DLPFC

### 2020-09-23 combined_analysis/diff.networks.Rmd
Update diff networks

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
---

@@

library(WGCNA)
library(variancePartition)
library(decorate)
library(ggrepel)
library(cowplot) 
library(metap) 
library(zenith) 
library(knitr) 
library(plyr) 
library(qvalue)  
library(BiocParallel)  
})   
source("../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

```{r load.data}
# Load data
resid.add = readRDS(synGet('syn22416489')$path)
vobj.lst = readRDS(synGet('syn22416446')$path)
METADATA = readRDS(synGet('syn22416411')$path)
METADATA$Reported_Gender = factor(METADATA$Reported_Gender, c("Male", "Female"))

@@

```{r load.WES}
df_schema = fread(synGet('syn22343823')$path)

@@

# ASD
df_asd = fread(synGet('syn22343811')$path)
colnames(df_asd)[colnames(df_asd)=="Q‑Val" ] = 'Q'
df_asd2 = data.frame(ENSEMBL = df_asd$Gene, Q = df_asd$Q)
df_asd2$chisq = qchisq(df_asd2$Q + 1e-15, 1, lower.tail=FALSE)
rownames(df_asd2) = df_asd2$ENSEMBL
```

```{r load.dream}
fit_marginal.lst = readRDS(synGet('syn22416500')$path)
fit_inter_sex.disease.lst = readRDS(synGet('syn22416524')$path)
df_meta = readRDS(synGet('syn22416508')$path)
df_meta.inter_sex.disease = readRDS(synGet('syn22416532')$path)
```

@@

@@

@@

rm(diff.net.Sex) # saving this to disk is slow, so just delete it

@@

@@

rm(net.Dx_Sex) # saving this to disk is slow, so just delete it

@@

```{r plot.meta.Dx_Sex}
ggplot(df_test_meta.Dx_Sex, aes(Module, -log10(P.Value))) + geom_bar(stat='identity', fill=df_test_meta.Dx_Sex$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + ylab(bquote(-log[10]~P)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")

@@

	plot_grid(fig1, fig2, fig3, ncol=1)
	})

@@

>>>>

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
upload: FALSE
---

@@

library(WGCNA)
library(variancePartition)
library(decorate)
library(ggrepel)
library(cowplot) 
library(metap) 
library(zenith) 
library(knitr) 
library(plyr) 
library(githubr)
library(qvalue)  
library(BiocParallel)  
})   
source("../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}

parentId = 'syn22416298';
activityName = 'Differential network analysis - DLPFC';
activityDescription = 'Differential network analysis - DLPFC';

thisFileName <- 'diff.networks.Rmd'

# Github link
thisRepo <- getRepo(repository = "CommonMindConsortium/covarr-de", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('combined_analysis/',thisFileName))
```

```{r load.data}
# Load data
resid.add = readRDS(synGet('syn22416489')$path)
vobj.lst = readRDS(synGet('syn22416446')$path)
METADATA = readRDS(synGet('syn22416411')$path)
ALL_USED_IDs = c('syn22416489', 'syn22416446', 'syn22416411')

METADATA$Reported_Gender = factor(METADATA$Reported_Gender, c("Male", "Female"))

@@

```{r load.WES}
df_schema = fread(synGet('syn22343823')$path)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn22343823')

@@

# ASD
df_asd = fread(synGet('syn22343811')$path)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn22343811')
colnames(df_asd)[colnames(df_asd)=="Q‑Val" ] = 'Q'
df_asd2 = data.frame(ENSEMBL = df_asd$Gene, Q = df_asd$Q)
df_asd2$chisq = qchisq(df_asd2$Q + 1e-15, 1, lower.tail=FALSE)
rownames(df_asd2) = df_asd2$ENSEMBL
```

```{r load.dream}
fit_marginal.lst = readRDS(synGet('syn22416500')$path)
fit_inter_sex.disease.lst = readRDS(synGet('syn22416524')$path)
df_meta = readRDS(synGet('syn22416508')$path)
df_meta.inter_sex.disease = readRDS(synGet('syn22416532')$path)

ALL_USED_IDs = c(ALL_USED_IDs, c('syn22416500', 'syn22416524', 'syn22416508', 'syn22416532'))
```

@@

# rm(diff.net) # saving this to disk is slow, so just delete it

@@

```{r save.network.null}
if( params$upload ){    
  # Code
  # Make sure these match the folder name and parent Id in the first chunk.
  CODE <- Folder(name = "Joint analysis of DLPFC count data", parentId = "syn22416298")
  CODE <- synStore(CODE)

  # Store data 
  save_network_results( diff.net, hcl, dynamicColors, df_test_null, "nullTest")
}
```

@@

# rm(diff.net.Sex) # saving this to disk is slow, so just delete it

@@

```{r save.network.Sex}
if( params$upload ){    
  # Code
  # Make sure these match the folder name and parent Id in the first chunk.
  CODE <- Folder(name = "Joint analysis of DLPFC count data", parentId = "syn22416298")
  CODE <- synStore(CODE)

  # Store data 
  save_network_results( diff.net.Sex, hcl, dynamicColors.Sex, df_test.Sex, "SexTest")
}
```

@@

# rm(net.Dx_Sex) # saving this to disk is slow, so just delete it

@@

```{r plot.meta.Dx_Sex, fig.width=5, fig.height}
ggplot(df_test_meta.Dx_Sex, aes(Module, -log10(P.Value))) + geom_bar(stat='identity', fill=df_test_meta.Dx_Sex$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + ylab(bquote(-log[10]~P)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")

@@

	plot_grid(fig1$fig_cor, fig2$fig_cor, fig3$fig_cor, nrow=1)
	plot_grid(fig1$fig_heatmap, fig2$fig_heatmap, fig3$fig_heatmap, nrow=1)
	plot_grid(fig1$fig_network, fig2$fig_network, fig3$fig_network, nrow=1)
	plot_grid(fig1$fig_cor, fig2$fig_cor, fig3$fig_cor, nrow=1)
	})

@@

```{r save.network.Dx_Sex}
if( params$upload ){    
  # Code
  # Make sure these match the folder name and parent Id in the first chunk.
  CODE <- Folder(name = "Joint analysis of DLPFC count data", parentId = "syn22416298")
  CODE <- synStore(CODE)

  # Store data 
  save_network_results( net.Dx_Sex, hcl, dynamicColors.Dx_Sex, df_test.Dx_Sex, "Dx_SexTest")
}
```
